
\begin{spverbatim}
Overall System Requirements

1. The system shall be comprised of two interactive web pages that should work on Chrome and Mozilla Firefox browsers for desktop and mobile. 
2. The system shall provide a home page as one of the two interactive web pages that contain an overview of the application's functionality.
4. The system shall provide a link from within the home page to the car prices estimation application page.
5. The system shall provide a link from the car prices estimation 
application page to the home page. 
6. The system shall be hosted using GitHub pages with the domain name www.estimatecarprices.github.io.
7. After the user deletes from an input field all input fields and displayed data below must be removed.
8. The user must be informed of any incorrect or unrelated input on any given input field.
9. The application should be minimalist and intuitive to use.

System Functional Requirements of the Home page.

1. The system shall upon loading display stock images that include captions describing the application and there should 
be a visible navigation bar.
2. The system shall describe the car makes that are supported by the application. 
3. The system shall provide a link at the bottom of the website that directs to the car price estimate application. 

System Functional Requirements of the car prices estimation application page.

1. The system shall upon loading provide an input box to enter vehicle make.
2. The system shall provide the user with different vehicle models depending on the vehicle make.
3. The system shall provide input fields for vehicle model year, available vehicle colors, and vehicle condition (New, Used).
4. The system should display a menu of options regarding vehicle mileage if the user selects a used vehicle.
5. The system shall then retrieve, the base price of a vehicle based on the model, year, and make. If the user selected a used vehicle the system shall accommodate the price which subtracts from the vehicle base price.
6. The system shall provide a button to calculate the final price of the vehicle based on the base price plus the color, vehicle condition, and year.
7. The system shall display the calculated price of the vehicle based on the user's input upon the user's click of a button.
\end{spverbatim}
